### Business Context

Nigeria's real-estate market is a strong African market use case because property decisions are high-value, location-sensitive, and affected by fragmented market information. A practical predictive workflow can help analysts answer questions such as:

- What is a reasonable estimated value for this listing?
- Which towns or states show strong market signals?
- Which property characteristics are associated with higher predicted value?
- Which listings require closer review because their market price differs materially from the model estimate?

### Stakeholders

The workflow is designed for business users and technical teams who need repeatable market intelligence:

- real estate investors;
- developers;
- property technology platforms;
- REIT-style analysts;
- banks and mortgage lenders;
- urban planners and market researchers.

### Dataset and Validation Evidence

The workshop dataset contains listing-level property information such as bedrooms, bathrooms, toilets, parking space, property type/title, town, state, and price. The workflow validates the incoming data before modeling so participants can see that machine learning starts with evidence about data quality.

```{r}
#| label: tbl-run-manifest
#| tbl-cap: Run governance summary

make_run_manifest_tbl(report_artifacts$run_manifest)
```

::: {.callout-note}
## Data validation principle

A model can only be as reliable as the data pipeline that feeds it. For this reason, the project includes `pointblank` validation output in `artifacts/reports/validation_report.html` and CSV summaries in `artifacts/metrics/`.
:::

### Market Intelligence Layer

The project also writes location-level summaries and exploratory figures. These outputs help bridge the technical model workflow and the business-growth story: pricing varies by geography, room configuration, and market concentration.

```{r}
#| label: fig-price-distribution
#| fig-cap: Property price distribution

safe_include_graphic("artifacts/figures/price_distribution.png", alt = "Property price distribution")
```

```{r}
#| label: fig-median-price-state
#| fig-cap: Median property price by state

safe_include_graphic("artifacts/figures/median_price_by_state.png", alt = "Median property price by state")
```
