### Modeling Strategy

The workflow compares a baseline linear regression model with stronger tree-based models. This is intentional for teaching: participants see why a transparent baseline matters, and they also see how random forest and XGBoost can capture non-linear market patterns.

The project keeps the baseline linear recipe separate from the tree-model recipe. Linear regression is more sensitive to redundant dummy variables and collinearity, while tree-based models can use a richer set of engineered predictors with less risk of rank-deficient fits.

### Model Comparison

@tbl-model-comparison ranks the trained models using test-set RMSE, MAE, and R-squared. These metrics are calculated on the log-transformed target, `log_price`, because housing prices are highly skewed.

```{r}
#| label: tbl-model-comparison
#| tbl-cap: Model comparison table

make_model_comparison_tbl(report_artifacts$model_comparison)
```

```{r}
#| label: fig-model-comparison
#| fig-cap: Model comparison by RMSE

safe_include_graphic("artifacts/figures/model_comparison_rmse.png", alt = "Model comparison RMSE plot")
```

### Prediction Quality

The actual-versus-predicted chart transforms predictions back from the log scale into Naira. This gives stakeholders a more intuitive view of model fit while retaining the modeling benefits of a log-transformed training target.

```{r}
#| label: fig-predicted-vs-actual
#| fig-cap: Actual versus predicted property prices

safe_include_graphic("artifacts/figures/predicted_vs_actual.png", alt = "Actual versus predicted property prices")
```

::: {.callout-note}
## Interpreting the prediction scale

The model learns `log_price`, but the stakeholder-facing prediction artifact uses `expm1(.pred)` to convert predictions back to the original price scale. This means `predicted_price`, `actual_price`, and `price_gap` in the business screening files are shown in Naira, not log units.
:::

### Feature Importance

Feature importance helps translate model behavior into business language. It gives participants a starting point for discussing whether location, property type, room structure, or parking capacity is driving estimated value.

```{r}
#| label: fig-feature-importance
#| fig-cap: Feature importance from the selected model

safe_include_graphic("artifacts/figures/feature_importance.png", alt = "Feature importance plot")
```
